PreProc2

### 2019-11-05 Notes.Rmd
quanteda startover

>>>>

packages to use

quanteda
readtext
spacyr

```{r}
install.packages("quanteda")
install.packages("readtext")
install.packages("spacyr")

```

# Loading in files using the readtext package
```{r}
require(readtext)

# Twitter json
dat_json <- readtext("~/Dropbox/QUANTESS/social media/zombies/tweets.json")
corp_twitter <- corpus(dat_json)
summary(corp_twitter, 5)
# generic json - needs a textfield specifier
dat_sotu <- readtext("~/Dropbox/QUANTESS/Manuscripts/collocations/Corpora/sotu/sotu.json",
                  textfield = "text")
summary(corpus(dat_sotu), 5)
# text file
dat_txtone <- readtext("~/Dropbox/QUANTESS/corpora/project_gutenberg/pg2701.txt", cache = FALSE)
summary(corpus(dat_txtone), 5)
# multiple text files
dat_txtmultiple1 <- readtext("~/Dropbox/QUANTESS/corpora/inaugural/*.txt", cache = FALSE)
summary(corpus(dat_txtmultiple1), 5)
# multiple text files with docvars from filenames
dat_txtmultiple2 <- readtext("~/Dropbox/QUANTESS/corpora/inaugural/*.txt",
                             docvarsfrom = "filenames", sep = "-",
                             docvarnames = c("Year", "President"))
summary(corpus(dat_txtmultiple2), 5)
# XML data
dat_xml <- readtext("~/Dropbox/QUANTESS/quanteda_working_files/xmlData/plant_catalog.xml",
                  textfield = "COMMON")
summary(corpus(dat_xml), 5)
# csv file
write.csv(data.frame(inaug_speech = texts(data_corpus_inaugural),
                     docvars(data_corpus_inaugural)),
          file = "/tmp/inaug_texts.csv", row.names = FALSE)
dat_csv <- readtext("/tmp/inaug_texts.csv", textfield = "inaug_speech")
summary(corpus(dat_csv), 5)
```

### 2019-11-05 preproc.Rmd
quanteda startover

set.seed(12345)
x = sample(1010242, 300000, replace = F)
#30% of data for training, 70% for testing
#due to hardware issues
train = news[x]
test = news[!x]
```

@@

```{r}
newsTDMHighFreq = findFreqTerms(newsTDM, lowfreq = 10000, highfreq = Inf)
inspect(newsTDM[newsTDMHighFreq, 1:10 ])
newsTDMHighFreq
```

```{r}
news.freq <- row_sums(newsTDM, na.rm=TRUE)
library(ggplot2)
#top 10 words -- counts
qplot(y = news.freq[order(news.freq, decreasing = T)][1:10], x = names(x = news.freq[order(news.freq, decreasing = T)][1:10]), ylab= "Frequency", xlab = "Word", main = "The top 10 words -- counts")
```

>>>>

set.seed(12345)
x = sample(1010242, 50000, replace = F)
#5% of data for training, 70% for testing
#due to hardware issues
train = news[x]
test = news[!x]
rm(con, news)
```

@@

```{r}
newsTDMHighFreq = findFreqTerms(newsTDM, lowfreq = 2500, highfreq = Inf)
inspect(newsTDM[newsTDMHighFreq, 1:10 ])
newsTDMHighFreq
```

```{r}
news.freq <- row_sums(newsTDM, na.rm=TRUE)
library(ggplot2)
#top 10 words -- counts
qplot(y = news.freq[order(news.freq, decreasing = T)][1:50], x = names(x = news.freq[order(news.freq, decreasing = T)][1:50]), ylab= "Frequency", xlab = "Word", main = "The top 50 words -- counts")
```

```{r}
news.freq[order(news.freq, decreasing = T)][1:50]
summary(news.freq)
```

```{r}
quantile4 = findFreqTerms(newsTDM, lowfreq = 5, highfreq = Inf)
names50 = names(news.freq[order(news.freq, decreasing = T)][1:50])
tdm = newsTDM[names50,]
tdm2 = newsTDM[quantile4, ]
tdm2.freq = row_sums(tdm2, na.rm = T)
tdm2.freq.ord = tdm2.freq[order(tdm2.freq, decreasing = T)]
summary(tdm2.freq)

```{r}
plot(tdm2.freq.ord[1:1000])
```
```{r}
tdm2.freq.log = log(tdm2.freq.ord)
plot(tdm2.freq.log)
```

```{r}
findAssocs(tdm2, "team", 0.05)
```
```{r}
findAssocs(tdm2, "season", 0.05)
```

Maybe I can use the 50 most used words to create <50 classes by checking the word associations with findAssocs() function. Then, If the word is found in one of the class set of words, that class weights will be used in the prediction algorithm.

*quanteda package*

### 2019-11-05 preproc2.Rmd
quanteda startover

---
title: "Main1"
author: "Yigit Ozan Berk"
date: "11/1/2019"
output: html_document
---

@@

```{r}
##orig.wd <- getwd()
##setwd("../final/en_US")
numwords <- system("wc -w *.txt", intern=TRUE)  # intern=TRUE to return output  
numlines <- system("wc -l *.txt", intern=TRUE)
numbytes <- system("wc -c *.txt", intern=TRUE)
# longest <- system("wc -L *.txt", intern=TRUE) # not working
##setwd(orig.wd)  # return to original working dir, ie. the parent of /final

>>>>

---
title: "PreProc2"
author: "Yigit Ozan Berk"
date: "11/5/2019"
output: html_document
---

@@

# init

```{r, init}
library(quanteda)
library(readtext)
library(spacyr)
```

```{r, numwords}

##orig.wd <- getwd()
##setwd("../final/en_US")
numwords <- system("wc -w *.txt", intern=TRUE)  # intern=TRUE to return output  
numlines <- system("wc -l *.txt", intern=TRUE)
numbytes <- system("wc -c *.txt", intern=TRUE)
# longest <- system("wc -L *.txt", intern=TRUE) # not working
##setwd(orig.wd)  # return to original working dir, ie. the parent of /final
